Cognate Priming

### 2023-09-12 docs/index.qmd
Clean git
Update

$$
\begin{aligned}
\textbf{Linear model:} \\
logit(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + \\
& (\beta_{1} + u_{1_{i}}) · \text{Age group}_{i} + & \\
& \beta_{2} · \text{Language Profile}_{i} + & \\
& (\beta_{3} + u_{2_{i}}) · \text{Trial type}_{i} + & \\
& \beta_{4} · (\text{Age group}_{i} \times \text{Language Profile}_{i}) & \\
& (\beta_{5} + u_{3_{i}}) · (\text{Age group}_{i} \times \text{Trial type}_{i}) + & \\
& \beta_{6} · (\text{Language Profile}_{ij} \times \text{Trial type}_{i}) & \\
& \beta_{7} · (\text{Age group}_{i} \times \text{Language Profile}_{i} \times \text{Trial type}_{i}) & \\
\end{aligned}
$$ {#eq-linear}

>>>>

$$
\begin{aligned}
\textbf{Linear model:} \\
\text{Logit}(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + (\beta_{1} + u_{1_{i}}) · \text{Age}_{i} + \beta_{2} · \text{Group}_{i} + & \\
& (\beta_{3} + u_{2_{i}}) · \text{Condition}_{i} + \beta_{4} · (\text{Age}_{i} \times \text{Group}_{i}) & \\
& (\beta_{5} + u_{3_{i}}) · (\text{Age}_{i} \times \text{Condition}_{i}) + \beta_{6} · (\text{Group}_{ij} \times \text{Condition}_{i}) & \\
& \beta_{7} · (\text{Age}_{i} \times \text{Group}_{i} \times \text{Condition}_{i}) & \\
\end{aligned}
$$ {#eq-linear}
